\documentclass[12pt]{article}

%
% Packages
%

\usepackage{etoolbox}
\usepackage[capposition=top]{floatrow}
\usepackage{graphicx}
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{placeins}
\usepackage{setspace}
\usepackage{array}
\usepackage{fullpage}
%\usepackage[margin=1.5in]{geometry}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{microtype}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{morefloats}
\usepackage{float}
\usepackage{caption}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{lmodern}

\hypersetup{
    colorlinks,
    linkcolor={black},
    citecolor={black},
    urlcolor={blue}
}
\usepackage{color,colortbl}
\usepackage{geometry}

\newcommand{\red}{\color{red}}
\newcommand{\blue}{\color{blue}}
\newtoggle{final}
%\togglefalse{final}
\toggletrue{final}


%
% Some utilities
%
%\usepackage{todonotes} % doesn't work - tikz lib too old
% define a mc=margincomment command
\iftoggle{final}{
   \newcommand{\mc}[2]{#1} % make margincomments go away
   \newcommand{\tc}[2]{#1} % make text comments go away
}%else
{
   \newcommand{\mc}[2]{% 1 referenced text 2 initials 3 comment
       \textcolor{blue}{#1}
       \marginpar{\scriptsize\textbf\raggedright\textcolor{red}{#2}}}
  \newcommand{\tc}[2]{\textcolor{blue}{#1}[\textcolor{red}{#2}]}
}

%
% Layout
%
\iftoggle{final}{
  \geometry{left=1.0in,right=1.0in,top=1.0in,bottom=1.0in}
}%else
{
  \geometry{left=0.5in,right=2.0in,top=1.0in,bottom=1.0in,marginparwidth=1.5in}
  }


\begin{document}

%Lane Adjustment Ahead: Uncertainty in Commuting Zones, Causes and Impacts
\title{Recalculating ... : How Uncertainty in Local Labor Market Definitions Affects Empirical Findings\thanks{The analysis, conclusions, and opinions expressed herein are those of the author(s) alone and do not necessarily represent the views of the U.S. Census Bureau or the Federal Deposit Insurance Corporation. All results have been reviewed to ensure that no confidential information is disclosed, and no confidential data was used in this paper. This document is released to inform interested parties of ongoing research and to encourage discussion of work in progress. Much of the work developing this paper occured while Mark Kutzbach was an employee of the U.S. Census Bureau.}}
\author[1]{Andrew Foote}
\author[2]{Mark J. Kutzbach}
\author[1,3]{Lars Vilhuber}
\affil[1]{Center for Economic Studies, U.S. Census Bureau}
\affil[2]{Federal Deposit Insurance Corporation}
\affil[3]{Labor Dynamics Institute, Cornell University}
\maketitle

\begin{center}
\textbf{[Preliminary Draft - Do not cite without authors' permission]}
\end{center}

\begin{abstract}

This paper evaluates the use of commuting zones as a local labor market definition. We revisit Tolbert and Sizer (1996) and demonstrate the sensitivity of definitions to two features of the methodology. We show how these features impact empirical estimates using a well-known application of commuting zones. We conclude with advice to researchers using commuting zones on how to demonstrate the robustness of empirical findings to uncertainty in definitions.
\end{abstract}


\doublespacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction \label{sec:intro}}
\input{./sections/mobz_intro.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Commuting Zone Data and Methodology \label{sec:method}}
\input{./sections/mobz_method.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Design Sensitivity \label{sec:dsens}}
\input{./sections/mobz_dsens.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Empirical Sensitivity \label{sec:esens}}
\input{./sections/mobz_esens.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion \label{sec:conclusion}}
\input{./sections/mobz_conclusion.tex}

%%%%%%%%%%%%%%%
% BIBLIOGRAPHY
%%%%%%%%%%%%%%%
\clearpage
\singlespacing

\bibliographystyle{aea}
\bibliography{bibliography}

\newpage
\appendix
\section*{Tables and Figures Appendix}
\FloatBarrier

\input{./sections/tab_fig_appendix.tex}





\end{document}
